---
title: "BetaTrend Profile"
author: "Noah Treutle"
date: "3/8/2022"
output: html_document
---

BetaTrendExplorations.Rmd

Most of the below code is adopted from SBIED lesson 4.

Don't run this chunk. We need to conduct more local searching of the likelihood surface for this be a valid approach. Instead we will use the MLE parameters from the original model as starting points.

```{r}
library(doParallel)
registerDoParallel()
```


## Conduct local search

```{r windows compatibility}
# added to make compatible with windows
if (Sys.info()[[7]] == "ntreu") {
  dir.create("tmp")
  options(pomp_cdir="./tmp")
}
```


```{r}
# loads prof_if which is an archive of mif2 searches from Anna??
load("C:/Users/ntreu/Downloads/adj_epi_mif.rda")
```



## testing option 1



```{r}
# guesses are the guesses of betat that we're searching
#box gives range of values for parameters

prof_if[,-c(1,2, 19,27, 28)] %>%
  filter(loglik>max(loglik)-20,loglik.se<2) %>%
  sapply(range) -> box

# S_0 ??
unfixed_param_names <- c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                         "nu", "rho", "tau", "E_0", "I_0", "sig_sq")

fixed_params <- coef(mod_1)[c("pop_0","mu", "delta", "sigma", "gamma", "alpha", "theta0", "A_0", "R_0")]

rw_sd1 <- rw.sd(beta1 = .02, beta2 = .02, beta3 = .02,
                    beta4 = .02, beta5 = .02, beta6 = .02,
                    tau = 0.02, rho = 0.02, nu = 0.02, sig_sq = 0.02,
                    E_0 = ivp(0.2), I_0 = ivp(0.2))

freeze(seed=1196696958,
  profile_design(
    betat=seq(-0.07,0.04,length=10),
    lower=box[1,unfixed_param_names],
    upper=box[2,unfixed_param_names],
    nprof=2, type="runif"
  )) -> guesses

library(doParallel)
library(doRNG)
library(parallel)
no_cores <- detectCores(logical=FALSE) 
cl<- parallel::makeCluster(no_cores)

# m2 is from the betatrendexplorations file
# needed the topline because of the str of
# mif2 requiring a special kind of object
# cl defined in betatrend exploration.Rmd
doParallel::registerDoParallel(cl)
registerDoRNG(123)
foreach(guess=iter(guesses,"row"), .combine=rbind) %dopar% {
  library(pomp)
  library(tidyverse)
  mod_1 %>%
    # problem is with params argument
    mif2(params=c(guess, fixed_params),
      rw.sd=rw_sd1, Nmif=50,cooling.fraction.50=0.5, Np=100) -> mf
  # replicate 10 runs of pfilter so we can get se's
  replicate(
    10,
    mf %>% pfilter(Np=100) %>% logLik()) %>%
    logmeanexp(se=TRUE) -> ll
  mf %>% coef() %>% bind_rows() %>%
    bind_cols(loglik=ll[1],loglik.se=ll[2])
}-> results
    

```


### Testing option 2
```{r}
# guesses are the guesses of betat that we're searching
#box gives range of values for parameters

prof_if[,-c(1,2, 19,27, 28)] %>%
  filter(loglik>max(loglik)-20,loglik.se<2) %>%
  sapply(range) -> box

# S_0 ??
unfixed_param_names <- c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                         "nu", "rho", "tau", "E_0", "I_0", "sig_sq")

fixed_params <- coef(mod_1)[c("pop_0","mu", "delta", "sigma", "gamma", "alpha", "theta0", "A_0", "R_0")]

rw_sd1 <- rw.sd(beta1 = .02, beta2 = .02, beta3 = .02,
                    beta4 = .02, beta5 = .02, beta6 = .02,
                    tau = 0.02, rho = 0.02, nu = 0.02, sig_sq = 0.02,
                    E_0 = ivp(0.2), I_0 = ivp(0.2))

freeze(seed=1196696958,
  profile_design(
    betat=seq(-0.07,0.04,length=10),
    lower=box[1,unfixed_param_names],
    upper=box[2,unfixed_param_names],
    nprof=2, type="runif"
  )) -> guesses

library(doParallel)
library(doRNG)
library(parallel)
no_cores <- detectCores(logical=FALSE) 
cl<- parallel::makeCluster(no_cores)

# m2 is from the betatrendexplorations file
# needed the topline because of the str of
# mif2 requiring a special kind of object
# cl defined in betatrend exploration.Rmd
doParallel::registerDoParallel(cl)
registerDoRNG(123)
#foreach(guess=iter(guesses,"row"), .combine=rbind) %dopar% {
foreach(i = 1:nrow(guesses), .combine=rbind) %dopar% {
  library(pomp)
  library(tidyverse)
  mod_1 %>%
    # problem is with params argument
    mif2(params=c(unlist(guesses[i,]),fixed_params, S_0 = 1 - guesses[i,"E_0"] - guesses[i,"I_0"]),
      rw.sd=rw_sd1, Nmif=50,cooling.fraction.50=0.5, Np=100) -> mf
  # replicate 10 runs of pfilter so we can get se's
  replicate(
    10,
    mf %>% pfilter(Np=100) %>% logLik()) %>%
    logmeanexp(se=TRUE) -> ll
  mf %>% coef() %>% bind_rows() %>%
    bind_cols(loglik=ll[1],loglik.se=ll[2])
}-> results
    

```


## Profile Check

```{r}
view(results)
```

```{r}
results %>% ggplot(aes(x = betat, y=loglik)) +
  geom_point() + geom_smooth()
```

## Profile Evaluation

```{r, eval = FALSE}
# guesses are the guesses of betat that we're searching
#box gives range of values for parameters
prof_if[,-c(1,2, 27, 28)] %>%
  filter(loglik>max(loglik)-20,loglik.se<2) %>%
  sapply(range) -> box

# S_0 ??
unfixed_param_names <- c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                         "nu", "rho", "tau", "E_0", "I_0", "sig_sq")

freeze(seed=1196696958,
  profile_design(
    betat=seq(-0.07,0.04,length=1000),
    lower=box[1,unfixed_param_names],
    upper=box[2,unfixed_param_names],
    nprof=15, type="runif"
  )) -> guesses
```



```{r}
(fixed_params <- coef(mod_1)[c("pop_0","mu", "delta", "sigma", "gamma", "alpha", "theta0", "S_0")])
coef(mod_1)
```

```{r}
# perturbing 12 parameters
#S_0 ??
rw_sd1 <- rw.sd(beta1 = .02, beta2 = .02, beta3 = .02,
                    beta4 = .02, beta5 = .02, beta6 = .02,
                    tau = 0.02, rho = 0.02, nu = 0.02, sig_sq = 0.02,
                    E_0 = ivp(0.2), I_0 = ivp(0.2))
```


```{r}
# m2 is from the betatrendexplorations file
# needed the topline because of the str of
# mif2 requiring a special kind of object
mf1 <- m2[[1]]
bake(file="betat_profile.rds",
  dependson=guesses,{
    library(doParallel)
    library(doRNG)
    # cl defined in betatrend exploration.Rmd
    registerDoParallel(cl, 4)
    registerDoRNG(830007657)
    foreach(guess=iter(guesses,"row"), .combine=rbind) %dopar% {
      library(pomp)
      library(tidyverse)
      mf1 %>%
        mif2(params=c(guess,fixed_params),
             # need to provide rw.sd for all unfixed params
          rw.sd=rw_sd1) %>%
        mif2(Nmif=100,cooling.fraction.50=0.5) -> mf
      # replicate 10 runs of pfilter so we can get se's
      replicate(
        10,
        mf %>% pfilter(Np=5000) %>% logLik()) %>%
        logmeanexp(se=TRUE) -> ll
      mf %>% coef() %>% bind_rows() %>%
        bind_cols(loglik=ll[1],loglik.se=ll[2])
    } -> results
    attr(results,"ncpu") <- getDoParWorkers()
    results
  }) -> results
```

