---
title: "BetaTrend Profile"
author: "Noah Treutle"
date: "3/8/2022"
output: html_document
---

BetaTrendExplorations.Rmd

Most of the below code is adopted from SBIED lesson 4.

Don't run this chunk. We need to conduct more local searching of the likelihood surface for this be a valid approach. Instead we will use the MLE parameters from the original model as starting points.

```{r}
library(doParallel)
registerDoParallel()
```


## Conduct local search

```{r windows compatibility}
# added to make compatible with windows
if (Sys.info()[[7]] == "ntreu") {
  dir.create("tmp")
  options(pomp_cdir="./tmp")
}
save(MODEL1_INPUT_PARAMETERS, file='model1params.rda')
```



```{r}
# loads prof_if which is an archive of mif2 searches from Anna??
load("C:/Users/ntreu/Downloads/adj_epi_mif.rda")
```



## testing option 1



```{r}
# guesses are the guesses of betat that we're searching
#box gives range of values for parameters

prof_if[,-c(1,2, 19,27, 28)] %>%
  filter(loglik>max(loglik)-20,loglik.se<2) %>%
  sapply(range) -> box

# S_0 ??
unfixed_param_names <- c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                         "nu", "rho", "tau", "E_0", "I_0", "sig_sq")

fixed_params <- coef(mod_1)[c("pop_0","mu", "delta", "sigma", "gamma", "alpha", "theta0", "A_0", "R_0")]

rw_sd1 <- rw.sd(beta1 = .02, beta2 = .02, beta3 = .02,
                    beta4 = .02, beta5 = .02, beta6 = .02,
                    tau = 0.02, rho = 0.02, nu = 0.02, sig_sq = 0.02,
                    E_0 = ivp(0.2), I_0 = ivp(0.2))

freeze(seed=1196696958,
  profile_design(
    betat=seq(-0.07,0.04,length=10),
    lower=box[1,unfixed_param_names],
    upper=box[2,unfixed_param_names],
    nprof=2, type="runif"
  )) -> guesses

library(doParallel)
library(doRNG)
library(parallel)
no_cores <- detectCores(logical=FALSE) 
cl<- parallel::makeCluster(no_cores)

# m2 is from the betatrendexplorations file
# needed the topline because of the str of
# mif2 requiring a special kind of object
# cl defined in betatrend exploration.Rmd
doParallel::registerDoParallel(cl)
registerDoRNG(123)
foreach(guess=iter(guesses,"row"), .combine=rbind) %dopar% {
  library(pomp)
  library(tidyverse)
  mod_1 %>%
    # problem is with params argument
    mif2(params=c(guess, fixed_params),
      rw.sd=rw_sd1, Nmif=50,cooling.fraction.50=0.5, Np=100) -> mf
  # replicate 10 runs of pfilter so we can get se's
  replicate(
    10,
    mf %>% pfilter(Np=100) %>% logLik()) %>%
    logmeanexp(se=TRUE) -> ll
  mf %>% coef() %>% bind_rows() %>%
    bind_cols(loglik=ll[1],loglik.se=ll[2])
}-> results
    

```


### Testing option 2
```{r}
# guesses are the guesses of betat that we're searching
#box gives range of values for parameters
load(adj_epi_mif.rda)
library(devtools)
devtools::install_github('hetankevin/haitipkg')
library(haitipkg)
mod_1 = haiti1mod()

prof_if[,-c(1,2, 19,27, 28)] %>%
  filter(loglik>max(loglik)-20,loglik.se<2) %>%
  sapply(range) -> box

# S_0 ??
unfixed_param_names <- c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                         "nu", "rho", "tau", "E_0", "I_0", "sig_sq")

fixed_params <- coef(mod_1)[c("pop_0","mu", "delta", "sigma", "gamma", "alpha", "theta0", "A_0", "R_0")]

rw_sd1 <- rw.sd(beta1 = .02, beta2 = .02, beta3 = .02,
                    beta4 = .02, beta5 = .02, beta6 = .02,
                    tau = 0.02, rho = 0.02, nu = 0.02, sig_sq = 0.02,
                    E_0 = ivp(0.2), I_0 = ivp(0.2))

freeze(seed=1196696958,
  profile_design(
    betat=seq(-0.07,0.04,length=10),
    lower=box[1,unfixed_param_names],
    upper=box[2,unfixed_param_names],
    nprof=2, type="runif"
  )) -> guesses

library(doParallel)
library(doRNG)
library(parallel)
no_cores <- detectCores(logical=FALSE) 
cl<- parallel::makeCluster(no_cores)

# m2 is from the betatrendexplorations file
# needed the topline because of the str of
# mif2 requiring a special kind of object
# cl defined in betatrend exploration.Rmd
doParallel::registerDoParallel(cl)
registerDoRNG(123)
#foreach(guess=iter(guesses,"row"), .combine=rbind) %dopar% {
foreach(i = 1:nrow(guesses), .combine=rbind) %dopar% {
  pars = c(unlist(guesses[i,]),fixed_params, S_0 = 1 - guesses[i,"E_0"] - guesses[i,"I_0"])
  parOrder = c("rho","tau","beta1","beta2","beta3","beta4","beta5","beta6","nu",
             "gamma","sigma","theta0","alpha","mu","delta","sig_sq","S_0","E_0",
             "I_0","A_0","R_0","pop_0","betat")
  pars = pars[order(factor(names(pars), levels = parOrder))]
  mod_1@params = pars
  library(pomp)
  library(tidyverse)
  #mod_1@params = c(unlist(guesses[i,]),fixed_params, S_0 = 1 - guesses[i,"E_0"] - guesses[i,"I_0"])
  mod_1 %>%
    # problem is with params argument
    mif2(
      rw.sd=rw_sd1, Nmif=200,cooling.fraction.50=0.5, Np=5000) -> mf
  # replicate 10 runs of pfilter so we can get se's
  replicate(
    100,
    mf %>% pfilter(Np=5000) %>% logLik()) %>%
    logmeanexp(se=TRUE) -> ll
  mf %>% coef() %>% bind_rows() %>%
    bind_cols(loglik=ll[1],loglik.se=ll[2])
}-> results
    
save(results, file = "trendResults.rda")

#m2 <- foreach(i=1:10,
#    .packages="pomp",.combine=c,.export=exl, .verbose=T) %dopar%
#    mif2(mod_1, Np=Np, Nmif=Nmif, rw.sd=rw_sd,
#         cooling.fraction.50=0.5)
#mod_1@params
results
```
Show in New Window
[1] 10
Show in New Window
         rho          tau        beta1        beta2        beta3        beta4        beta5        beta6           nu        gamma 
3.148019e-01 3.767802e+02 5.332350e+00 2.656585e+00 3.832467e+00 2.766603e+00 5.097354e+00 1.803385e+00 9.840841e-01 3.500000e+00 
       sigma       theta0        alpha           mu        delta       sig_sq          S_0          E_0          I_0          A_0 
5.000000e+00 0.000000e+00 2.397300e-03 4.287000e-04 1.433000e-04 1.016082e-01 9.985646e-01 2.147751e-06 1.433240e-03 0.000000e+00 
         R_0        pop_0        betat 
0.000000e+00 1.091182e+07 0.000000e+00 

## Profile Check

```{r}
view(results)
results
```

```{r}
results
results %>% 
  group_by(betat) %>%
  summarize(loglik=max(loglik)) %>%
  ggplot(aes(x = betat, y=loglik)) +
  geom_point() + geom_smooth()

pchisq(-2*(-2731 - -2721.153), 11)
       
results$loglik %>% max
```

```{r}
mcap(results$loglik, results$betat)[7][1]$fit %>%
  group_by(parameter) %>%
  summarize(smoothed=max(smoothed)) %>%
  ggplot(aes(x = -parameter, y=smoothed)) +
  geom_point() + geom_smooth() + 
  geom_vline(xintercept = -mcap(results$loglik, results$betat, confidence = 0.9)$ci[1])  +
    geom_vline(xintercept = -mcap(results$loglik, results$betat, confidence = 0.9)$ci[2])

scatter(mcap(results$loglik, results$betat)$smooth_fit)

plot(mcap(results$loglik, results$betat)[7]$parameter, mcap(results$loglik, results$betat)[7]$smoothed)
mcap(results$loglik, results$betat)[7][1]$fit

mcap(results$loglik, results$betat)$mle
```

go re-estimate all parameters and profile on joint epi, end dataset

## Profile Evaluation

```{r, eval = FALSE}
# guesses are the guesses of betat that we're searching
#box gives range of values for parameters
prof_if[,-c(1,2, 27, 28)] %>%
  filter(loglik>max(loglik)-20,loglik.se<2) %>%
  sapply(range) -> box

# S_0 ??
unfixed_param_names <- c("beta1", "beta2", "beta3", "beta4", "beta5", "beta6",
                         "nu", "rho", "tau", "E_0", "I_0", "sig_sq")

freeze(seed=1196696958,
  profile_design(
    betat=seq(-0.07,0.04,length=1000),
    lower=box[1,unfixed_param_names],
    upper=box[2,unfixed_param_names],
    nprof=15, type="runif"
  )) -> guesses
```



```{r}
(fixed_params <- coef(mod_1)[c("pop_0","mu", "delta", "sigma", "gamma", "alpha", "theta0", "S_0")])
coef(mod_1)
```

```{r}
# perturbing 12 parameters
#S_0 ??
rw_sd1 <- rw.sd(beta1 = .02, beta2 = .02, beta3 = .02,
                    beta4 = .02, beta5 = .02, beta6 = .02,
                    tau = 0.02, rho = 0.02, nu = 0.02, sig_sq = 0.02,
                    E_0 = ivp(0.2), I_0 = ivp(0.2))
```


```{r}
# m2 is from the betatrendexplorations file
# needed the topline because of the str of
# mif2 requiring a special kind of object
mf1 <- m2[[1]]
bake(file="betat_profile.rds",
  dependson=guesses,{
    library(doParallel)
    library(doRNG)
    # cl defined in betatrend exploration.Rmd
    registerDoParallel(cl, 4)
    registerDoRNG(830007657)
    foreach(guess=iter(guesses,"row"), .combine=rbind) %dopar% {
      library(pomp)
      library(tidyverse)
      mf1 %>%
        mif2(params=c(guess,fixed_params),
             # need to provide rw.sd for all unfixed params
          rw.sd=rw_sd1) %>%
        mif2(Nmif=100,cooling.fraction.50=0.5) -> mf
      # replicate 10 runs of pfilter so we can get se's
      replicate(
        10,
        mf %>% pfilter(Np=5000) %>% logLik()) %>%
        logmeanexp(se=TRUE) -> ll
      mf %>% coef() %>% bind_rows() %>%
        bind_cols(loglik=ll[1],loglik.se=ll[2])
    } -> results
    attr(results,"ncpu") <- getDoParWorkers()
    results
  }) -> results
```

