---
title: "FOI Exploration"
author: "Noah Treutle"
date: "2/9/2022"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(pomp)
#library(haitipkg)
library(doParallel)
library(doRNG)
library(gridExtra)
library(devtools)
library(lubridate)
load_all('/Users/hetankevin/Library/CloudStorage/OneDrive-Personal/Documents/UMich/Research/haitiRes/haitipkg')
knitr::opts_chunk$set(echo = TRUE)
```

```{r run levels}
# set run levels
Nsim <- 1000
```

## Epidemic FOI Exploration
```{r pomp def}
results
epi_mod_1 <- haiti1mod()
#epi_mod_1@params = 
  
  
tempres = (results[which.max(results$loglik),] %>% unlist)[1:23]
#tempres[23] = 0

epi_mod_1@params = tempres
epi_mod_1@params
```


```{r simulate mod_1}
# simulates the model and stores results in df called epi_sims
simulate(epi_mod_1,nsim=Nsim,seed=1643079359, 
         format="data.frame", include.data = TRUE) -> epi_sims

epi_sims %>% filter(week > 300)
epi_sims

```

Disclaimer: Had to set include.data = TRUE in order to get parameter values for the simulations >>> why?

```{r}
# remove case data

pf = epi_mod_1 %>% pfilter(params = results[which.max(results$loglik),] %>% unlist, 
                           Np=5000, save.states=TRUE) 

projfilt = project_from_filter2(epi_mod_1, pf) 

projfilt %>% group_by(week) %>% summarize(cases = quantile(cases, c(0.025, 0.5, 0.975), 
                                                           na.rm=TRUE), q = c('low', 'median', 'high')) %>%
  pivot_wider(names_from=q, values_from=cases) %>% mutate(
    date_week_start = ymd(paste0(2010, "-10-23")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d")) %>%
  ggplot() + geom_line(aes(x=week_date, y=median)) + 
  geom_ribbon(aes(x=week_date, ymin=low, ymax=high), fill='darkgreen', alpha=0.4) + 
  labs(title = "Fixed Model Projected Cases", x='Date', y='Cases')

projfilt %>% group_by(week) %>% mutate(cases=log(cases)) %>% summarize(cases = quantile(cases, c(0.025, 0.5, 0.975), 
                                                           na.rm=TRUE), q = c('low', 'median', 'high')) %>%
  pivot_wider(names_from=q, values_from=cases) %>% mutate(
    date_week_start = ymd(paste0(2010, "-10-23")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d")) %>%
  ggplot() + geom_line(aes(x=week_date, y=median)) + 
  geom_ribbon(aes(x=week_date, ymin=low, ymax=high), fill='darkgreen', alpha=0.4) + 
  labs(title = "Fixed Model Projected Cases on Log Scale", x='Date', y='Log Cases')
#epi_sims <- epi_sims %>% dplyr::filter(ifelse(.id == "data", FALSE, TRUE))
```


```{r no-vaccine FOI}
epi_sims <- epi_sims %>% mutate(N = S+E+I+A+R, 
                       beta = exp(epi_mod_1@params[['beta1']]*seas1 +
                         epi_mod_1@params[['beta2']]*seas2 + 
                         epi_mod_1@params[['beta3']]*seas3 + 
                         epi_mod_1@params[['beta4']]*seas4 + 
                         epi_mod_1@params[['beta5']]*seas5 + 
                         epi_mod_1@params[['beta6']]*seas6 +
                           epi_mod_1@params[['betat']]*((week-215)/430)))
# setup lambda
epi_sims <- epi_sims %>% mutate(lambda = (I)^epi_mod_1@params[['nu']] * (beta/N))

```


```{r}

epi_sims %>% group_by(week) %>% summarize(cases = quantile(cases, c(0.025, 0.5, 0.975), 
                                                           na.rm=TRUE), q = c('low', 'median', 'high')) %>%
  pivot_wider(names_from=q, values_from=cases) %>% cbind(actual=agg$cases) %>% mutate(
    date_week_start = ymd(paste0(2010, "-10-23")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d")) %>%
  ggplot() + geom_line(aes(x=week_date, y=median)) +
  geom_point(aes(x=week_date, y=actual)) + 
  geom_ribbon(aes(x=week_date, ymin=low, ymax=high), fill='darkgreen', alpha=0.4) + 
  labs(title = "Fixed Model Simulated Cases vs Actual Cases", x='Date', y='Cases')

epi_sims %>% group_by(week) %>% mutate(cases = log(cases+1)) %>% summarize(cases = quantile(cases, c(0.025, 0.5, 0.975), 
                                                           na.rm=TRUE), q = c('low', 'median', 'high')) %>%
  pivot_wider(names_from=q, values_from=cases) %>% cbind(actual=agg$cases+1) %>% mutate(
    date_week_start = ymd(paste0(2010, "-10-23")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d")) %>%
  mutate(actual = log(actual)) %>%
  ggplot() + geom_line(aes(x=week_date, y=median)) +
  geom_point(aes(x=week_date, y=actual)) + 
  geom_ribbon(aes(x=week_date, ymin=low, ymax=high), fill='darkgreen', alpha=0.4) + 
  labs(title = "Fixed Model Simulated Cases vs Actual Cases on Log Scale", x='Date', y='Log Cases')

agg = haiti1_agg_data()
```

```{r}
epi_sims %>% group_by(week) %>% summarize(beta = quantile(beta, c(0.025, 0.5, 0.975), 
                                                           na.rm=TRUE), q = c('low', 'median', 'high')) %>%
  pivot_wider(names_from=q, values_from=beta) %>% mutate(
    date_week_start = ymd(paste0(2010, "-10-23")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d")) %>%
  ggplot() + geom_line(aes(x=week_date, y=median)) +
  geom_ribbon(aes(x=week_date, ymin=low, ymax=high), fill='darkgreen', alpha=0.4) + 
  labs(title = expression("Fixed Model Simulated "*beta*'(t)'), x='Date', y=expression(beta(t)))



epi_sims %>% group_by(week) %>% summarize(lambda = quantile(lambda, c(0.025, 0.5, 0.975), 
                                                           na.rm=TRUE), q = c('low', 'median', 'high')) %>%
  pivot_wider(names_from=q, values_from=lambda) %>% mutate(
    date_week_start = ymd(paste0(2010, "-10-23")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d")) %>%
  ggplot() + geom_line(aes(x=week_date, y=median)) +
  geom_ribbon(aes(x=week_date, ymin=low, ymax=high), fill='darkgreen', alpha=0.4) + 
  labs(title = expression("Fixed Model Simulated "*lambda*'(t)'), x='Date', y=expression(lambda(t)))


```

```{r}
                                                           
haitiRainfall %>%
  pivot_longer(
    data = .,
    cols = -date,
    names_to = 'dep',
    values_to = 'rainfall'
  ) %>%
  mutate(
    year = year(date),
    week = week(date)
  ) %>%
  group_by(year, week) %>%
  summarize(national_weekly_rain = sum(rainfall)) %>%
  ungroup() %>% # Not needed, but good practice
  mutate(
    date_week_start = ymd(paste0(2010, "-10-23")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d")) %>% group_by(week) %>% 
  summarize(national_weekly_rain = quantile(national_weekly_rain, c(0.025, 0.5, 0.975), 
                                                           na.rm=TRUE), q = c('low', 'median', 'high')) %>%
  pivot_wider(names_from=q, values_from=national_weekly_rain)  %>%
  ggplot() + geom_line(aes(x=week, y=median)) +
  geom_ribbon(aes(x=week, ymin=low, ymax=high), fill='darkgreen', alpha=0.4) + 
  labs(title = expression("Weekly Rainfall from 2010-2019"), x='Week', y='Rainfall (mm)')


epi_sims %>% group_by(week) %>% summarize(beta = quantile(beta, c(0.025, 0.5, 0.975), 
                                                           na.rm=TRUE), q = c('low', 'median', 'high')) %>%
  pivot_wider(names_from=q, values_from=beta) %>% mutate(
    date_week_start = ymd(paste0(2010, "-10-23")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d"),
    Year=as.factor(year(week_date))) %>% group_by(week) %>% group_by(Year) %>% 
  ggplot() + geom_line(aes(x=week(week_date), y=median, group=year(week_date), color=Year)) + 
  labs(title = expression("Fixed Model Simulated "*beta*'(t)'), x='Week', y=expression(beta(t)))
```


```{r plot prep}
# Take median of lambda for each week and store in a vector
epi_med_lambda <- c()

for(i in c(1:430)) {
  epi_med_lambda[i] <- median(filter(epi_sims, week==i)$lambda, na.rm=TRUE)
}

week <- c(1:430)
epi_lambdas <- data.frame(epi_med_lambda, week)


epi_med_beta = c()

for(i in c(1:430)) {
  epi_med_beta[i] <- median(filter(epi_sims, week==i)$beta)
}

epi_med_cases = c()
for(i in c(1:430)) {
  epi_med_cases[i] <- median(filter(epi_sims, week==i)$cases)
}

epi_betas <- data.frame(epi_med_beta, week)
epi_cases <- data.frame(epi_med_cases, week)
epi_cases

(epi <- epi_lambdas %>% ggplot(aes(x = week, y = epi_med_lambda)) + geom_point() + labs(title = "Fixed Model Simulated Median FOI by Week", 
                                                                                        x='Week', y=expression(lambda(t))))

epi_betas %>% ggplot(aes(x = week, y = epi_med_beta)) + geom_point() + labs(title = "Fixed Model Simulated Median Beta by Week", 
                                                                                 x='Week', y=expression(beta(t)))

epi_cases %>% ggplot(aes(x = week, y = epi_med_cases)) + geom_point() + labs(title = "Fixed Model Simulated Median Cases by Week",
                                                                             x='Week', y='Simulated Median Cases')
```




## Endemic FOI Exploration
```{r}
end_mod_1 <- haiti1(period = "endemic")
```


```{r}
# simulates the model and stores results in df called end_sims
simulate(end_mod_1,nsim=Nsim,seed=1643079359, 
         format="data.frame", include.data = TRUE) -> end_sims
```

Disclaimer: Had to set include.data = TRUE in order to get parameter values for the simulations >>> why?

```{r}
# remove case data
end_sims <- end_sims %>% dplyr::filter(ifelse(.id == "data", FALSE, TRUE))
```


```{r}
end_sims <- end_sims %>% mutate(N = S+E+I+A+R, 
                       beta = end_mod_1@params[['beta1']]*seas1 +
                         end_mod_1@params[['beta2']]*seas2 + 
                         end_mod_1@params[['beta3']]*seas3 + 
                         end_mod_1@params[['beta4']]*seas4 + 
                         end_mod_1@params[['beta5']]*seas5 + 
                         end_mod_1@params[['beta6']]*seas6)
# setup lambda
kappa <- 0.95
end_sims <- end_sims %>% mutate(lambda = (I + (1-kappa)*A)^end_mod_1@params[['nu']] * (beta/N))
```



Take median of lambda for each week and store in a vector

```{r}
end_med_lambda <- c()

for(i in c(233:430)) {
  end_med_lambda[i-232] <- median(filter(end_sims, week==i)$lambda)
}

end_week <- c(233:430)
end_lambdas <- data.frame(end_med_lambda, end_week)

```


```{r}
epi_med_beta = c()
end_med_beta <- c()

for(i in c(1:232)) {
  epi_med_beta[i] <- median(filter(epi_sims, week==i)$beta)
}

for(i in c(233:430)) {
  end_med_beta[i-232] <- median(filter(end_sims, week==i)$beta)
}


week <- c(1:232)
epi_betas <- data.frame(epi_med_beta, week)

end_week <- c(233:430)
end_betas <- data.frame(end_med_beta, end_week)

```

fit variable no. of backshift operators




### Endemic Sims Median FOI by Week

```{r}
(end <- end_lambdas %>% ggplot(aes(x = end_week, y = end_med_lambda)) + geom_point() + labs(title = "Endemic Sims Median FOI by Week"))
```
```{r}
(end <- end_lambdas %>% ggplot(aes(x = end_week, y = end_med_lambda)) + geom_point() + labs(title = "Epidemic Sims Median FOI by Week"))
epi_mod_1@params

end_med_lambda

end_lambdas
```


### Epidemic Sims Median FOI by Week



```{r}

epi_betas %>% mutate(date = lubridate::ymd("2010-10-16") + lubridate::weeks(week)) %>%
  filter(date < "2012-01-01", date >= "2011-01-01") %>% ggplot() + 
  geom_line(aes(x = date, y =  exp(log(epi_med_beta)-1e-5*week)))
  
end_sims$S %>% plot()


epi_sims %>% group_by(week) %>% summarize(S = mean(S)) %>% plot
end_sims$I
epi_sims %>% group_by(week) %>% summarize(S = mean(S, na.rm=TRUE)) %>% plot
epi_sims %>% group_by(week) %>% summarize(R = mean(R, na.rm=TRUE)) %>% plot
results
```

?pfilter



### Case Data Plot

```{r, include=FALSE}
#load("~/Haiti Research/haitipkg/data/haitiCholera.rda")
load("../haitipkg/data/haitiCholera.rda")
```


### Explore case totals

```{r}
# add total case count
haitiCholera %>% mutate(totals = Artibonite+Centre+Grand.Anse+Nippes+Nord
                           + haitiCholera[,7]+haitiCholera[,8]+Ouest+Sud+haitiCholera[,11]) -> haitiCholera
```

```{r}
epi_cases <- haitiCholera[c(1:232),] %>% ggplot()+
  geom_line(aes(x = c(1:232), y = unlist(totals))) + labs(title="Epidemic Cases")
```


```{r}
end_cases <- haitiCholera[c(233:426),] %>% ggplot()+
  geom_line(aes(x = c(233:426), y = unlist(totals))) + labs(title="Endemic Cases")
```



```{r}
grid.arrange(epi, epi_cases)
```



```{r}
grid.arrange(end, end_cases)
```
```{r}
sic_codes = sec.all.sic()
```


```{r}

sec.all.sic <- function (run.all.sic = F, incl.otc = F)
{
   require(XML)
   require(httr)
   strip.white <- function(x)
       gsub("^ *|(?<= ) | *$", "", x, perl = TRUE)
   curr.time <- Sys.time()
   curr.time <- gsub(" ", "\\.", curr.time)
   curr.time <- gsub(":", "\\.", curr.time)
   log.file <- paste("log.", curr.time, ".txt", sep = "")
   write(as.character(Sys.time()), log.file, append = F)
   if(run.all.sic | !file.exists("SIC.Codes.txt"))
       try.sic <- 100:9999
   else
{
   try.sic <- read.delim("SIC.Codes.txt", header = F, as.is = T)
   try.sic <- as.matrix(try.sic)
   try.sic <- as.numeric(try.sic[, 1])
}
take <- try.sic < 1000
try.sic[take] <- paste(0, try.sic[take], sep = "")
mat <- c("CIK", "Name", "SIC", "Industry", "Location")
for(ix in try.sic)
{
   get.pg <- T
   print(paste("Processing ", ix, sep = ""))
   s <- 0
   while(get.pg)
   {
url <- paste( "https://www.sec.gov/cgi-bin/browse-edgar?action=getcompany&SIC=", ix, "&owner=include&match=&start=",
s, "&count=100", "&hidefilings=0", sep = "")
       x <- sec.get.webpage(url)
       y <- sec.parse.html(x, keyword = "div")
       y1 <- grep(paste("SIC ", ix, sep = ""), y)
       y2 <- grep(paste("SIC: ", ix, sep = ""), y)
       if(length(y1) > 0)
       {
          y <- y[y1]
          y <- unlist(strsplit(y, paste("SIC ", ix, " - ",
              sep = "")))[2]
          ind <- unlist(strsplit(y, " Click on CIK"))[1]
          x <- sec.parse.html(x, keyword = "table")
          x <- x[-(1:3)]
          cik <- !is.na(as.numeric(x))
          z <- matrix("", sum(cik), 5)
          j <- 0
          for(i in 1:length(x))
          {
              if(cik[i])
                 z[j <- j + 1, 1] <- x[k <- i]
              else if(i == k + 1)
                 z[j, 2] <- strip.white(x[i])
              else if(i == k + 2)
                 z[j, 5] <- x[i]
          }
          z[, 3] <- ix
          z[, 4] <- ind
          mat <- rbind(mat, z)
          get.pg <- nrow(z) == 100
       }
       else if(length(y2) > 0)
       {
          z <- rep("", 5)
          y1 <- grep("CIK#: ", y)
          y1 <- y[y1[1]]
          y1 <- unlist(strsplit(y1, " CIK#: "))
          z[2] <- strip.white(y1[1])
          y1 <- y1[2]
          z[1] <- unlist(strsplit(y1, " "))[1]
          y2 <- grep("SIC: ", y)
          y2 <- y[y2[1]]
          y2 <- unlist(strsplit(y2, paste("SIC: ",
             ix, " - ", sep = "")))[2]
          y2 <- unlist(strsplit(y2, "State location: "))
          z[4] <- y2[1]
          y2 <- unlist(strsplit(y2[2], " "))
          z[5] <- y2[1]
          z[3] <- ix
          mat <- rbind(mat, z)
          get.pg <- F
} else
get.pg <- F
s <- s + 100 }
   }
   sec.write.table(mat, "SIC.Download.txt", T)
   write(as.character(Sys.time()), log.file, append = T)
   sec.sic(incl.otc = incl.otc)
}



sec.dump <- function ()
{
   x <- sapply(ls(pos = 1), function(x) storage.mode(get(x)))
   y <- names(x)[x == "function"]
   z <- grep("sec\\.", y)
   y <- y[z]
   save(list = y, file = "SEC.RData")
   dump(y, "sec.code.txt")
}
sec.fix.names <- function(x, drop.suffix, drop.last = T)
{
x <- toupper(x)
x <- gsub("D/B/A", "", x)
x <- gsub("\\.COM", " COM", x)
x <- gsub(",", "", x)
x <- gsub("\'", "", x)
x <- gsub("\\.", "", x)
x <- gsub(";", "", x)
x <- gsub("\\(", "", x)
x <- gsub("\\)", "", x)
x <- gsub("/", " ", x)
x <- gsub("!", " ", x)
x <- gsub("&AMP", "AND", x)
x <- gsub("&", "AND", x)
x <- gsub("-", " ", x)
x<-gsub(" ","",x)
x <- gsub("CORPORATION", "CORP", x)
x <- gsub("^ *|(?<= ) | *$", "", x, perl = TRUE)
if(!drop.last)
   return(x)
for(i in 1:length(x))
{
   while(drop.last){
       y <- unlist(strsplit(x[i], " "))
       if(y[1] == "THE")
          y <- y[-1]
       n <- length(y)
       z <- y[n]
       drop.last <- any(z == drop.suffix) & n > 1
       if(drop.last)
       {
} }
x[i] <- y[1]
if(n > 2)
   for(j in 2:(n - 1))
       x[i] <- paste(x[i], y[j], sep = " ")
       drop.last <- T
   }
return(x) }


sec.get.webpage <- function (url)
{
   response <- try(GET(url))
   if(mode(response) == "list")
   {
       x <- unlist(response)
       x <- grep("status_code", x)
       if(length(x) == 1)
          if(response$status_code != 200)
              print(c(url, ",
                 http status = ", response$status_code))
   }
   u <- htmlParse(response, useInternalNodes = T, asText = T)
   webpage <- as(u, "character")
   webpage <- readLines(tc <- textConnection(webpage))
   close(tc)
   return(webpage)
}


sec.match <- function (a, b)
{
   x <- match(a, b)
   x <- x[!is.na(x)]
   return(x)
}


sec.nasdaq.ticker <- function (x)
{
if(vec.x <- is.vector(x))
   x <- as.matrix(x, length(x), 1)
   y <- x[, 1]
   take <- nchar(y) == 5
   if(sum(take) == 0)
   {
       if(vec.x)
          x <- as.vector(x)
return(x) }
   z <- y[take]
   for(i in 1:length(z))
   {
       v <- unlist(strsplit(z[i], ""))
       if(any(v[5] == c("G","H","I","R","T","V","W","X")))
          z[i] <- "99999"
   }
   y[take] <- z
   x[, 1] <- y
   bad <- y == "99999"
   x <- x[!bad, ]
   if(vec.x)
       x <- as.vector(x)
   return(x)
}


sec.nq.amex <- function (db)
{
   y <- sec.read.nq(db$file.nq.amex)
   y <- sec.nyse.ticker(y)
   db$tickers.nq.amex <- as.character(y[, 1])
   db$mkt.cap.nq.amex <- as.character(y[, 2])
   db$last.nq.amex <- as.numeric(y[, 3])
   db$exch.nq.amex <- rep("A", nrow(y))
   db$name.nq.amex <- as.character(y[, 4])
}
sec.nq.nasdaq <- function (db)
{
   y <- sec.read.nq(db$file.nq.nasdaq)
   y <- sec.nasdaq.ticker(y)
   db$tickers.nq.nasdaq <- as.character(y[, 1])
   db$mkt.cap.nq.nasdaq <- as.character(y[, 2])
   db$last.nq.nasdaq <- as.numeric(y[, 3])
   db$exch.nq.nasdaq <- rep("Q", nrow(y))
   db$name.nq.nasdaq <- as.character(y[, 4])
}
sec.nq.nyse <- function (db)
{
   y <- sec.read.nq(db$file.nq.nyse)
   y <- sec.nyse.ticker(y)
   db$tickers.nq.nyse <- as.character(y[, 1])
   db$mkt.cap.nq.nyse <- as.character(y[, 2])
   db$last.nq.nyse <- as.numeric(y[, 3])
   db$exch.nq.nyse <- rep("N", nrow(y))


db$name.nq.nyse <- as.character(y[, 4])
}
sec.nt.nasdaq <- function (db)
{
   x <- sec.read.nt(db$file.nt.nasdaq)
   y <- x[, c("Symbol", "Test.Issue")]
   y <- sec.nasdaq.ticker(y)
   test <- y[, 2] == "Y"
   db$tickers.nt.nasdaq <- y[!test, 1]
   db$exch.nt.nasdaq <- rep("Q", length(db$tickers.nt.nasdaq))
   db$test.tickers.nt.nasdaq <- y[test, 1]
}
sec.nt.other <- function (db)
{
   x <- sec.read.nt(db$file.nt.other)
   exch <- x[, "Exchange"]
   exch[exch == "P"] <- "N"
   x[, "Exchange"] <- exch
   y <- x[, c("CQS.Symbol", "Exchange", "Test.Issue")]
   y <- sec.nyse.ticker(y)
   test <- y[, 3] == "Y"
   db$tickers.nt.other <- y[!test, 1]
   db$exch.nt.other <- y[!test, 2]
   db$test.tickers.nt.other <- y[test, 1]
}
sec.nyse.ticker <- function (x)
{
   if(vec.x <- is.vector(x))
       x <- as.matrix(x, length(x), 1)
   y <- x[, 1]
   z <- gsub("[A-Z]", "", y)
   take <- z == "" | z == "/"
   y[!take] <- "99999"
   for(i in 1:length(y))
   {
       z <- unlist(strsplit(y[i], "/"))
       if(length(z) == 2)
          if(nchar(z[2]) > 1)
              y[i] <- "99999"
          else
              y[i] <- paste(z[1], z[2], sep = ".")
   }
   x[, 1] <- y
   bad <- y == "99999"
   x <- x[!bad, ]
   if(vec.x)
       x <- as.vector(x)
   return(x)
}


sec.osha <- function () {
    require(XML)
    require(httr)
    get.ind <- function(id, code) {
      url <- paste(
          "https://www.osha.gov/pls/imis/sic_manual.display?id=",
          id, "&tab=group", sep = "")
      y <- sec.get.webpage(url)
      x <- sec.parse.html(y, keyword = "div")
      y1 <- grep(paste("Industry Group ", code, "*.:", sep = ""), x)[1]
      y2 <- grep("SIC Search Division Structure", x)[1]
      x <- x[y1:(y2-1)]
      z <- c("Code", "Industry Group", "Industry")
      for(i in 1:length(x)) {
         if(length(grep("Industry Group", x[i])) > 0) {
             u <- unlist(strsplit(x[i], " "))
             u <- u[-(1:3)]
             for(j in 1:length(u))
                if(j == 1)
                   ind.grp <- u[1]
                else
                   ind.grp <- paste(ind.grp, u[j], sep = " ")
        } 
        else {
          v <- unlist(strsplit(x[i], " "))
          code <- v[1]
          ind <- gsub(paste(code, " ", sep = ""), "", x[i])
          z <- rbind(z, c(code, ind.grp, ind))
        } 
      }
      return(z) 
    }
    url <- "https://www.osha.gov/pls/imis/sic_manual.html"
    y <- sec.get.webpage(url)
    x <- sec.parse.html(y, keyword = "div")
    y1 <- grep("SIC Division Structure", x)[1]
    y2 <- grep("Major Group 99", x)[1]
    x <- x[(y1+1):y2]
    z <- c("Code", "Division", "Major Group", "Industry Group", "Industry") 
    for(i in 1:length(x)) {
       u <- unlist(strsplit(x[i], ": "))
       if(length(grep("Division", u[1])) > 0)
           div <- u[2]
       else {
        maj <- u[2]
        code <- unlist(strsplit(u[1], " "))[3]
                  v <- grep(paste("Major Group ", code, sep = ""), y)
                  v <- y[v]
                  v <- unlist(strsplit(v, "id="))[2]
                  id <- unlist(strsplit(v, "&amp"))[1]
                  q <- get.ind(id, code)
                  q <- cbind(q[, 1], rep(div, nrow(q)), rep(maj, nrow(q)),
                      q[, 2:3])
                  q <- q[-1, ]
                  z <- rbind(z, q)
      }
    }
   sec.write.table(z, "SIC.table.txt", T)
}


sec.parse.html <- function (webpage, keyword)
{
   pagetree <- htmlTreeParse(webpage, error=function(...){},
       useInternalNodes = TRUE)
   # parse the tree
   x <- xpathSApply(pagetree, paste("//*/", keyword, sep = ""), xmlValue)
   if(!is.character(x))
       return(keyword)
   # do some clean up with regular expressions
   x <- unlist(strsplit(x, "\n"))
   x <- gsub("\t","",x)
   x <- sub("^[[:space:]]*(.*?)[[:space:]]*$", "\\1", x, perl=TRUE)
   x <- x[!(x %in% c("", "|"))]
   return(x)
}


sec.read.nq <- function (file)
{
   x <- read.csv(file = file, header = T, strip.white = T, sep = ",")
   x <- as.matrix(x)
   mode(x) <- "character"
   x1 <- sec.strip.white(x)
   y <- x1[, c("Symbol", "MarketCap", "LastSale")]
   y <- cbind(y, x[, "Name"])
   return(y)
}

sec.read.nt <- function (file) {
  x <- readLines(file)
  x <- gsub("\'", "", x)
  file <- paste(file, ".cleaned.txt", sep = "")
  write(x, file = file)
  x <- read.table(file = file, sep = "|", header = T, comment.char = "@",
         fill = T, strip.white = T)
  x <- as.matrix(x)
  mode(x) <- "character"
  test <- x[, "Test.Issue"]
  bad <- test == ""
  x <- x[!bad, ]
  return(x)
}

sec.sic <- function (incl.otc = F)
{
   fund.etc <- function(x)
   {
       if(length(grep("FUND", x)) > 0)
          return(T)
       if(length(grep("TRUST", x)) > 0)
          return(T)
       if(length(grep("PORTFOLIO", x)) > 0)
          return(T)
       if(length(grep("ETF", x)) > 0)
          return(T)
       if(length(grep("INCOME", x)) > 0)
          return(T)
       if(length(grep("DIVIDEND", x)) > 0)
          return(T)
       if(length(grep("SHARES", x)) > 0)
          return(T)
       if(length(grep("DIVIDEND", x)) > 0)
          return(T)
       if(length(grep(" BOND", x)) > 0)
          return(T)
       if(length(grep(" RETURN", x)) > 0)
          return(T)
       if(length(grep(" SECURITIES", x)) > 0)
          return(T)
       if(length(grep(" INVESTMENT", x)) > 0)
          return(T)
       if(length(grep(" INVESTOR", x)) > 0)
          return(T)
       if(length(grep(" MUNICIPAL", x)) > 0)
          return(T)
       if(length(grep(" GROWTH", x)) > 0)
          return(T)
       if(length(grep(" INFLATION", x)) > 0)
          return(T)
       if(length(grep(" VOLATILITY", x)) > 0)
          return(T)
       if(length(grep("DOW 30", x)) > 0)
          return(T)
       if(length(grep("TREASURY", x)) > 0)
          return(T)
       if(length(grep("CONTINGENT", x)) > 0)
          return(T)
       if(length(grep("FLOATING", x)) > 0)
          return(T)
       if(length(grep(" RATE", x)) > 0)
          return(T)
       if(length(grep("INDEX", x)) > 0)
          return(T)
return(F)
}
drop.suffix <- c("INC", "INCORPORATED", "LP", "CORPORATION",
   "CORP", "PLC", "LTD", "LIMITED", "COMPANY", "AG", "SA",
   "LLC", "PLLC", "DBA", "THE", "NEW", "NV", "HOLDING",
   "HOLDINGS", "CO", "HLDGS", "HLDG", "PARTNERSHIP")
drop.suffix <- c(drop.suffix, state.abb[])
u <- read.delim("SIC.Codes.txt", header = F)
u <- as.matrix(u)
sic.names <- u[, 2]
names(sic.names) <- sic.codes <- as.character(u[, 1])
w <- read.delim("SIC.Download.txt", header = T)
w <- as.matrix(w)
mode(w) <- "character"
sec.names <- sec.fix.names(w[, 2], "", drop.last = F)
sec.sic.codes <- w[, 3]
db <- new.env()
db$file.nq.amex = "NQ_AMEX.csv"
db$file.nq.nyse = "NQ_NYSE.csv"
db$file.nq.nasdaq = "NQ_NASDAQ.csv"
db$file.nt.other = "NT_otherlisted.txt"
db$file.nt.nasdaq = "NT_nasdaqlisted.txt"
sec.nq.amex(db)
sec.nq.nyse(db)
sec.nq.nasdaq(db)
sec.nt.other(db)
sec.nt.nasdaq(db)
sec.tickers(db)
tickers <- db$tickers
co.names <- sec.fix.names(db$name, "", drop.last = F)
exch <- db$exch.nq
cap <- db$mkt.cap.nq
if(incl.otc)
{
   x <- read.csv("otctickers.csv", header = T)
   x <- as.matrix(x)
   tickers <- c(tickers, x[, 1])
   co.names <- c(co.names,
        sec.fix.names(x[, 10], "", drop.last = F))
   exch <- c(exch, x[, 4])
   cap <- c(cap, rep(NA, nrow(x)))
}
n <- length(tickers)
sic <- c("TICKER", "EXCH", "SIC", "SIC.NAME", "MKT.CAP")
no.sic <- c("TICKER", "EXCH", "MKT.CAP", "FUND.ETC", "NO.MATCH")
for(i in 1:n)
{
   take <- co.names[i] == sec.names
   x <- unique(sec.sic.codes[take])
   if(length(x) == 1)
   {
       sic <- rbind(sic,
          c(tickers[i], exch[i], x, sic.names[x], cap[i]))
next

       }
       co.name <- sec.fix.names(co.names[i], drop.suffix)
       y <- grep(co.name, sec.names)
       if(length(y) == 0)
       {
          no.sic <- rbind(no.sic,
              c(tickers[i], exch[i], cap[i], fund.etc(co.name),
"TRUE"))
next }
       sec.name <- sec.fix.names(sec.names[y], drop.suffix)
       sec.sic.code <- sec.sic.codes[y]
       take <- co.name == sec.name
       if(sum(take) == 0)
       {
          no.sic <- rbind(no.sic,
              c(tickers[i], exch[i], cap[i], fund.etc(co.name),
                 "TRUE"))
next }
       x <- unique(sec.sic.code[take])
       if(length(x) > 1)
       {
          no.sic <- rbind(no.sic,
              c(tickers[i], exch[i], cap[i], fund.etc(co.name),
"FALSE"))
next }
       sic <- rbind(sic,
          c(tickers[i], exch[i], x, sic.names[x], cap[i]))
   }
   y <- unique(sic[-1, 3])
   ind <- matrix(0, k <- nrow(sic) - 1, length(y))
   for(i in 1:k)
       ind[i, ] <- as.numeric(sic[i + 1, 3] == y)
   dimnames(ind)[[1]] <- sic[-1, 1]
   dimnames(ind)[[2]] <- y
   sec.write.table(sic, file = "TICKER.SIC.txt", last.return = T)
   sec.write.table(no.sic, file = "NO.SIC.txt", last.return = T)
   write.table(ind, file = "SIC.IND.CLASS.txt", quote = F, sep = "\t")
}
sec.strip.white <- function (x)
{
   x <- gsub("\t", "", x)
   x <- gsub(" ", "", x)
   return(x)
}
sec.tickers <- function (db)
{
   db$tickers.nq <- c(db$tickers.nq.amex, db$tickers.nq.nyse,
       db$tickers.nq.nasdaq)
   db$exch.nq <- c(db$exch.nq.amex, db$exch.nq.nyse, db$exch.nq.nasdaq)


db$mkt.cap.nq <- c(db$mkt.cap.nq.amex, db$mkt.cap.nq.nyse,
   db$mkt.cap.nq.nasdaq)
db$last.nq <- c(db$last.nq.amex, db$last.nq.nyse, db$last.nq.nasdaq)
db$name.nq <- c(db$name.nq.amex, db$name.nq.nyse, db$name.nq.nasdaq)
db$tickers.nt <- c(db$tickers.nt.other, db$tickers.nt.nasdaq)
db$exch.nt <- c(db$exch.nt.other, db$exch.nt.nasdaq)
db$test.tickers.nt <- c(db$test.tickers.nt.other,
   db$test.tickers.nt.nasdaq)
x <- sec.match(db$test.tickers.nt, db$tickers.nq)
db$tickers.nq <- db$tickers.nq[-x]
db$exch.nq <- db$exch.nq[-x]
db$mkt.cap.nq <- db$mkt.cap.nq[-x]
db$last.nq <- db$last.nq[-x]
db$name.nq <- db$name.nq[-x]
db$tickers <- db$tickers.nq
db$name <- db$name.nq
}
sec.write.table <- function (x, file, last.return = F)
{
   if(last.return)
   {
       write.table(x, file = file, quote = F, row.names = F,
          col.names = F, sep = "\t")
return(1) }
   single.line <- F
   if(is.matrix(x))
       if(nrow(x) == 1)
          single.line <- T
   if(is.vector(x))
       single.line <- T
   if(single.line)
   {
       write.table(x, file = file, quote = F, row.names = F,
          col.names = F, sep = "\t", eol = "")
return(1) }
   y <- x[nrow(x), ]
   x <- x[-nrow(x), ]
   z <- y[1]
   if(length(y) > 1)
       for(i in 2:length(y))
          z <- paste(z, "\t", y[i], sep = "")
   write.table(x, file = file, quote = F, row.names = F,
       col.names = F, sep = "\t")
   write.table(z, file = file, quote = F, row.names = F,
       col.names = F, sep = "\t", eol = "", append = T)
}

```







