---
title: "Rainfall"
author: "Noah Treutle"
date: '2022-04-19'
output: html_document
---

```{r}
library(haitipkg)
library(tidyverse)
library(lubridate)
```

Rainfall is summmed rainfall from Haiti's 10 departments. Each line represents a different year. The rainfall is likely in mm. Weekly national rainfall seems inconsistent with google saying weekly national average is ~200mm. Will have to specify how we calculated weekly national rainfall. Data source is NASA, looks like you need to register for an account to get the data.

```{r}
df <- haitiRainfall %>%
  pivot_longer(
    data = ., 
    cols = -date,
    names_to = 'dep',
    values_to = 'rainfall'
  ) %>%
  mutate(
    year = year(date),
    week = week(date)
  ) %>%
  group_by(year, week) %>%
  summarize(national_weekly_rain = sum(rainfall)) %>%
  ungroup() %>% # Not needed, but good practice
  mutate(
    date_week_start = ymd(paste0(2014, "-01-01")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d")
  )
# Be weary of beggining and end, because of way things were rounded. 
df %>%
  filter(week != 1, week != max(week)) %>% 
  ggplot(aes(x = week_date, y = national_weekly_rain, group = year, col = as.factor(year))) + 
  geom_line() + 
  theme_bw() + 
  guides(color = 'none') + 
  scale_x_date(date_labels = "%b", date_breaks = '1 month') + 
  ylab('Weekly National Rain (mm)') + 
  theme(axis.title.x = element_blank())

```




```{r}
df1 <- haitiRainfall %>%
  pivot_longer(
    data = ., 
    cols = -date,
    names_to = 'dep',
    values_to = 'rainfall'
  ) %>%
  mutate(
    year = year(date),
    week = week(date)
  ) %>%
  group_by(year, week) %>%
  summarize(national_weekly_rain = sum(rainfall)) %>%
  ungroup() %>% # Not needed, but good practice
  group_by(week) %>%
 summarize(median_rainfall = median(national_weekly_rain, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(
    date_week_start = ymd(paste0(2014, "-01-01")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d")
  ) 
```


















```{r}

# Be weary of beggining and end, because of way things were rounded. 
df1 %>%
  filter(week != 1, week != max(week)) %>% 
  ggplot(aes(x = week_date, y = mean_rainfall), color= "blue") + 
  geom_line(color="blue") + 
  geom_area(fill="light blue")
  theme_bw() + 
  guides(color = 'none') + 
  scale_x_date(date_labels = "%b", date_breaks = '1 month') + 
  ylab('Weekly Mean National Rain (mm)') + 
  theme(axis.title.x = element_blank())

```

```{r}
df3 <- df %>%
  filter(week != 1, week != max(week)) 

# Be weary of beggining and end, because of way things were rounded. 
df1 %>%
  filter(week != 1, week != max(week)) %>% 
  ggplot(aes(x = week_date, y = median_rainfall), color= "blue") + 
  geom_line(color="blue") + 
  theme_bw() + 
  guides(color = 'none') + 
  scale_x_date(date_labels = "%b", date_breaks = '1 month') + 
  ylab('Weekly Median National Rain (mm)') + 
  theme(axis.title.x = element_blank())



```





```{r}
df2 <- haitiRainfall %>%
  pivot_longer(
    data = ., 
    cols = -date,
    names_to = 'dep',
    values_to = 'rainfall'
  ) %>%
  mutate(
    year = year(date),
    week = week(date)
  ) %>%
  group_by(year, week) %>%
  summarize(national_weekly_rain = sum(rainfall)) %>%
  ungroup() %>% # Not needed, but good practice
  group_by(week) %>%
 summarize(median_rainfall = median(national_weekly_rain, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(
    date_week_start = ymd(paste0(2014, "-01-01")) + weeks(week - 1),
    week_date = as.Date(date_week_start, format = "%m-%d")
  )
```



```{r}
df2 <- df %>%
  
```


```{r}
median_rainfall <- df1$median_rainfall
df[,6] <- rep(0, nrow(df))
colnames(df)[6] <- "median_rainfall"


```



```{r}
for(i in 1:nrow(df)) {
  for(j in 1:length(median_rainfall))
    if(df[i,"week"] == j) {
      df[i,"median_rainfall"] <- median_rainfall[j]
  }
}

```



```{r}
df[]
```


```{r}
df <- df
```


```{r}
df %>%
  filter(week != 1, week != max(week)) %>% 
  ggplot(aes(x = week_date, y = national_weekly_rain, group = year, col = as.factor(year))) + 
  geom_line() + 
  #geom_line(aes(y = median_rainfall))
  theme_bw() + 
  guides(color = 'none') + 
  scale_x_date(date_labels = "%b", date_breaks = '1 month') + 
  ylab('Weekly National Rain (mm)') + 
  theme(axis.title.x = element_blank())
```













```{r}
df3 <- df %>%
  filter(week != 1, week != max(week)) 

# Be weary of beggining and end, because of way things were rounded. 
df1 %>%
  filter(week != 1, week != max(week)) %>% 
  ggplot(aes(x = week_date, y = median_rainfall, color=median_rainfall)) + 
  geom_line(aes(color = "blue"),color= "blue", size = 3) + 
  theme_bw() + 
  guides(color = 'none') + 
  scale_x_date(date_labels = "%b", date_breaks = '1 month') + 
  ylab('Weekly National Rainfall (mm)') + 
  theme(axis.title.x = element_blank()) +
  geom_line(data = df3, aes(x = week_date, y = national_weekly_rain, group = year, color = as.factor(year)))
```



```{r}
df3 <- df %>%
  filter(week != 1, week != max(week)) 

df4 <-df1 %>%
  filter(week != 1, week != max(week)) 
# Be weary of beggining and end, because of way things were rounded. 

ggplot()+
  geom_line(data = df3, aes(x = week_date, y = national_weekly_rain, group = year, col = as.factor(year))) +
  guides(color = 'none') + 
  ggplot(data= df4, aes(x = week_date, y = median_rainfall)) +
  ggplot(aes(x = week_date, y = median_rainfall)) +
  geom_line(aes(color = "blue"),color="blue", size = 3) + 
 # theme_bw() + 
  scale_x_date(date_labels = "%b", date_breaks = '1 month') + 
  ylab('Weekly National Rainfall (mm)') + 
  theme(axis.title.x = element_blank()) 
```


